---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Sara Kolaczyk"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
library(scales)
ggplot(covid_data_count, aes(x = date, y = Cases)) + stat_summary(aes(color = race), fun = mean, geom = "line") + scale_y_continuous(labels = label_number(suffix = "K", scale = 1/1000), breaks = seq(0, 400000, by = 200000)) + theme(legend.title = element_blank()) + labs(title = "Average Covid Cases by Race") + theme(plot.title = element_text(hjust = 0.5))
```


If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe? 

I am plotting the average number of cases by race over time. There is an overall increase in cases between April and January 

2. Are there any conclusions you can draw?

From April to January the White cases increase more rapidly than other cases

3. What were you not able to do due to not having the R knowledge?

I was not able to remove the "total" cases and alter the axes to have a clearer view of the output for each specific race. 

4. What other data would be useful to better understand this data?

gender and age were missing from all four data sets and would be useful to analyze. 
